---
title: "Final Project 302 Yunya Li"
author: ""
subtitle: ""
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

# Introduction
. This study will be dedicated to analyzing the association between soccer players’ wage and value, age, league, and position on the field, among data of all active players information provided by FIFA in 2022.


## The relation between Age and wage


```{r age, message=F}
# pdf_document: default

library(tidyverse)
library(patchwork)

dat <- read_csv("players_22.csv")

#Histogram of Player ages
pagehist<-ggplot(data = dat, aes(age)) +
  # step 2 add a histogram with custom breaks to match old graph
  geom_histogram(aes(y=..density..),breaks=seq(15, 55, by=2), colour = 1, fill = "white") +
  geom_density (lwd = 1, colour = 4,
               fill = 4, alpha = 0.25)+
  theme_bw()+
  labs(
   # title = "Histogram and Density of Player Ages",
    x="Player Ages",
    y=""
  )

dat = mutate(dat, age_rank = ntile(desc(dat$age),5))
 
pageboxplot<-ggplot(data = dat, aes(x=as.factor(age_rank),y=wage_eur)) +
  # step 2 add a histogram with custom breaks to match old graph
  geom_boxplot()+
  theme_bw()+
  ylim(0,30000)

pagehist+pageboxplot

aovwageage<-aov(formula=wage_eur~as.factor(age_rank), data = dat)
aovwageage
```


## The five major European football leagues 

```{r fivemajor, message=F}

Eurotop5<-c("Italian Serie A" ,"English Premier League" ,"French Ligue 1" ,
           "German 1. Bundesliga" , "Spain Primera Division")   

dat$Eurotop5<-ifelse(dat$league_name %in% Eurotop5,1,0)
dat$Eurotop5<-as.factor(dat$Eurotop5)

ggplot(data = dat, aes(x=wage_eur)) +
  # step 2 add a histogram with custom breaks to match old graph
  #geom_histogram(aes(y=..density..,fill=Eurotop5),alpha=0.25) +
  geom_density (aes(y=..density..,fill=Eurotop5,color=Eurotop5),lwd = 1,
                alpha = 0.25)+
  theme_bw()+
  labs(
   # title = "Histogram and Density of Player Ages",
    #x="Player Ages",
    y=""
  )+
  xlim(0,50000)
  
staEurotop5<-t.test(x=dat$wage_eur[dat$Eurotop5=="1"], y=dat$wage_eur[dat$Eurotop5=="0"], alternative = "greater", var.equal = FALSE)

staEurotop5
#staEurotop5$statistic


```


```{r position, message=F}

ggplot(data = dat, aes(x=club_position,y=wage_eur)) +
  # step 2 add a histogram with custom breaks to match old graph
  #geom_histogram(aes(y=..density..,fill=Eurotop5),alpha=0.25) +
  geom_boxplot()+ #geom_violin ()+
  theme_bw()+
  labs(
   # title = "Histogram and Density of Player Ages",
    #x="Player Ages",
    y=""
  )+
  ylim(0,20000)
 
aovposition<-aov(formula=wage_eur~club_position, data = dat)
aovposition

```
 The F test rejects the null hypothesis, and there is no difference in the income of each position

## Correlation analysis

```{r Correlation, message=F}
library(GGally)

ggpairs(dat[, c("wage_eur", "value_eur", "potential","overall")])
```
From the correlation between wage and value, potential and overall, the correlation coefficient between wage and value is 0.824, showing the strongest correlation. The correlation coefficient between wage and overall is 0.602, and the correlation is the second. The correlation coefficient between wage and potential is 0.498, which is the lowest correlation, but also a strong positive correlation.


```{r linear model, message=F}
#Histogram of Player ages
library(MASS)
b <- boxcox(lm(wage_eur ~ 1,data=dat))
# Exact lambda
lambda <- b$x[which.max(b$y)]
lambda

dat$boxcoxwage<-(dat$wage_eur^lambda-1)/lambda

ggplot(data = dat, aes(x=boxcoxwage ) )+
  # step 2 add a histogram with custom breaks to match old graph
  geom_histogram(aes(y=..density..),breaks=seq(15, 55, by=2), colour = 1, fill = "white") +
  geom_density (lwd = 1, colour = 4,
               fill = 4, alpha = 0.25)+
  theme_bw()+
  labs(
   # title = "Histogram and Density of Player Ages",
    #x="Player Ages",
    y=""
  )

ml1<-lm(formula = wage_eur~value_eur+potential+overall+club_position+Eurotop5+as.factor(age_rank),data=dat)

ml2<-lm(formula = boxcoxwage~value_eur+potential+overall+club_position+Eurotop5+as.factor(age_rank),data=dat)

#step(object=ml2,direction = "forward")

plot(ml1,2)
plot(ml2,2)

summary(ml2)

knitr::kable(summary(ml2)$coefficients)
#summary(ml2)$coefficients

```


